\documentclass{article}

% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Computer Lab Project Report}
\author{Harsimran Singh}

\begin{document}
\maketitle

\begin{abstract}
The report showcase my computer lab projects that i had built to make my CV and Website. I built this to showcase my skiils that i had learned in my lectures.I had used HTML language, Latex and Github pages to built my Portfolio. This report Outlines my limitation, what i learned and what Improvements i need to do make more attractive in future. It will also show live link of my website and my github link to easily access.
\end{abstract}

\section{Introduction}

The goal of this project report was to create personal portfolio website to show my CV , Projects and skills online. in the modern era , a digital portfolio is must to showcase our skills which can also help us to get job and can also attract recruiters .I hosted my website for d=free using github pages.This report show what i learned while doing my project and what can i do for improvement. 



\section{Portfolio URL and GitHub Repository}

\begin{itemize}
    \item \textbf{Live Portfolio Website:} \url{https://singhunique.github.io/}
    \item \textbf{GitHub Repository:} \url{https://github.com/singhunique/singhunique.github.io}
\end{itemize}

\section{Tools and Technologies Used}
I had used some tools and technologies as well to develop my project.
\begin{itemize}
    \item \textbf{Latex}: used for creating professional CV and also project Report 
    \item \textbf{GitHub}: used for code repository 
    \item \textbf{Overleaf}:Used for online latex editor
    \item \textbf{Visual code}: Used for writing HTML code
    \item \textbf{GitHub pages}:Used to host personal portfolio website.
\end{itemize}
\section{Reflection}

\subsection{Strengths}
\begin{itemize}
    \item Created professional and clean portfolio which shows my skills and projects  
    \item the website navigation is simple and clear 
\end{itemize}

\subsection{Challenges} 
\begin{itemize}
    \item Designing an attractive website was a major challenge for me as i created this first time in my career
    \item Embedding the PDF CV on website was a difficult challenge for  me
\end{itemize}

\subsection{Future Improvements}
\begin{itemize}
    \item i want to add some colors and fonts to enchnave the beauty of my website
    \item Add some videos  to make more attractive website.
\end{itemize}    

\section{Conclusion}
In this project i learned many new things in my career for the first time . It helps me to Built my own personal portfolio webiste using many tools. There are only some improvements to focus which can help me to make my website even more better. This project Demonstrates me to show my ability to independently work on my projects in future which can be valuable for my career as well. 

\section{References}

\begin{itemize}
    \item My live portfolio website: \url{https://singhunique.github.io/}
    \item My GitHub repository: \url{https://github.com/singhunique/harsimran_portfolio}
    \item LaTeX documentation: \url{https://www.latex-project.org/help/documentation/}
    \item GitHub Pages documentation: \url{https://docs.github.com/en/pages}
\end{itemize}



\end{document}
